%%%%%%%%%%%%%%%%%%%%%% glossary.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Working glossary for the monograph shell; terms stressed in Chapter~8.
%%%%%%%%%%%%%%%%%%%%%%%% Springer Nature %%%%%%%%%%%%%%%%%%%%%%%%%

\Extrachap{Glossary}

\runinhead{Asset-ID}
Abbreviation, after first explanation, for the stable asset identifier of a maintainable host in the facility register and twin. Language answers and CMMS tickets must name the same code; temporary image filenames are not substitutes.

\runinhead{Asset passport}
Compact, asset-centred retrieval unit that aggregates recent observations, geometry or severity summaries, and explicit neighbour lists for one Asset-ID.

\runinhead{Bounded agent}
Tool-using LLM procedure that may read twin memory and draft actions, but must pass human and geofence gates before writes or revisits.

\runinhead{Cite-or-abstain}
Generation contract requiring every named Asset-ID or observation ID in an answer to appear in the retrieved evidence package; otherwise the system abstains.

\runinhead{Decision-ready twin}
Semantic twin that additionally exposes observation cards, topology for propagation reading, and interfaces that retrieval and tools can call.

\runinhead{Model harness}
Code-owned control layer around a replaceable LLM: intake, evidence assembly, typed tools, validators, traces, and write gates.

\runinhead{Observation record}
One defect sighting with modality tag, time stamp, detector signature, openable imagery pointer, and host Asset-ID attachment.

\runinhead{Retrieval-augmented generation (RAG)}
Query-time loading of editioned manuals or observation cards so answers are grounded outside parametric model weights.
